% !TEX root = ../thesis_main.tex
\chapter{Conclusions}

In this work we extended the implicit-solvent model of electrostatics implemented in \pygbe \cite{CooperClementiBarba2015}
to study nanoplasmonics in the quasistatic limit for applications in biosensing \cite{ClementiETal2017, ClementiETal2019}.
We applied this model to simulations of localized surface plasmon resonance, where we computeded the extinction cross section of 
conductive nanoparticles and computed the shift in the resonance frequency when having biomolecules in the vicinity of the 
nanoparticle.

\textbf{Contributions of this work}

We developed an open source boundary integral solver for computational nanoplasmonics in the quasistatic limit. We extended \pygbe to work 
with complex values, and added the functionality needed to solve localized surface plasmon resonance problems. \pygbe 
counts with an algorithmic acceleration with a treecode, and hardware acceleration with GPUs, making this solver 
suitable to compute problems of at least half a million boundary elements, which is required to represent the solvent excluded 
surface of the biomolecule accurately.

We verified our solver against an analytical solution based on the Mie theory for silver nanospheres (section \ref{sec:verification}), and 
presented convergence studies for our results which builds confidence on the suitability of our boundary integral model and the  
correctness of or solver. 
We performed a sensitivity study of an LSPR biosensor model by computing the resonance-frequency shift
while varying the distance between the nanoparticle and the biomolecules. We showed that our boundary element methods approach in
the quasistatic limit, is able to capture the characteristic behavior of LSPR biosensors (section \ref{sec:lspr_response_bsa}).

We explored different reduced-order models for the protein, and showed that geometries like ellipsoids and spheres
to model the protein are not accurate compared to using a meshed constructed from the crystal structure of the protein. Even though
none of these models were accurate, the volume equivalent ellipsoidal model performed better compared to the surface based ellipsoidal 
model and the volume equivalent sphere. Using volume equivalent ellipsoids for the protein representation 
translated to fast computations, that even if they were not accurate, they served as great candidates to explored the different components of the 
computational model of the biosensor. We used this model to shine light on the effects of multiple factors such us 
the orientation, the presence charges in the protein, the number of proteins, and the effect of the incoming electric field \ref{sec:ell_study}.
We found that using real dielectrics for the protein and the embedding medium does not affect the shift in the resonance frequency, 
as long as they are averaged values from the real part of the original complex data, but it does affect the intensity of the extinction 
cross section, which is a problem if the results are intended to be used for sensitivity calculations \ref{sec:diel_study}. 
These reduced-order models, despite not being accurate compared to the full protein model, provide fast computed insights that can be used 
in the exploratory stage on the design or study of biosensors.

We matched and replicated the findings of computational results in the general area of nanostructure responses to electromagnetic waves from 
from Rockstuhl et al. \cite{rockstuhl2005} and Ellis et al.\cite{ellis2016} (section \ref{sec:rep_rockstuhl} and \ref{sec:rep_val_ellis}). We validated \pygbe against experimental results of reflectance 
of localized surface phonon polariton (SPhP) nanostructures from Ellis et al. (section \ref{sec:rep_val_ellis}). Both replication and validation 
studies were hard to achieve due to insufficient data and experiments and/or simulation details, and we stated that the lack of reproducible open
practices is the reason for it. We concluded that open reproducible practices are needed not only to guarantee the work published is possible 
to reproduce, but also for replicability and validation studies. 

All of the results of this work along with the materials needed to reproduce or replicate them, were made publicly available in the form of 
reproducibility packages (sections \ref{sec:repro_lspr}, \ref{sec:repro_ell}, and \ref{sec:repro_val}). The nanoplasmonics extension of \pygbe, and 
the results of this work, can offer a valuable computational approach for the future studies on the field, and aid in the design of LSPR biosensors as well as SPhP based sensors. 


